# Setup Env

```{r include=FALSE}
library(tidyverse)
library(cowplot)
library(ggpubr)
```

# Map

```{r}
library(ggOceanMaps)
library(grid)
library(sf)
library(ggspatial)

# .ggOceanMapsenv <- new.env() ## set new environment to save shape file
# .ggOceanMapsenv$datapath <- "./Data/dd_rbathy_cont.rda"

notenclosed <- read_sf("C:/Users/klynch/OneDrive - Marine Institute of Memorial University (1)/Thesis/Manu_1/Code/Chap1/Data/NAFO_Divisions_SHP/NAFO_Divisions_2021_line_not_enclosed.shp")
JKsubocean <- notenclosed %>% filter(Division == "2J"|Division == "3K") 
Lsubocean <- notenclosed %>% filter(Division == "3L")

poly <- read_sf("C:/Users/klynch/OneDrive - Marine Institute of Memorial University (1)/Thesis/Manu_1/Code/Chap1/Data/NAFO_Divisions_SHP/NAFO_Divisions_2021_poly_clipped.shp")
JKsubpoly <- poly %>% filter(Division == "2J"|Division == "3K")
Lsubpoly <- poly %>% filter(Division == "3L")

acsurv <- read_sf("C:/Users/klynch/OneDrive - Marine Institute of Memorial University (1)/Thesis/Manu_1/Code/Chap1/Data/Survey_Area/general_survey_area.shp")

```
## - Figure 1
```{r, fig.width=5, fig.height=5}
load("./Data/nlbasemap.RData")

map <-  nlmap +
  geom_spatial_text(aes(x = -50, y = c(53.5, 51, 47.5), label = c("2J","3K","3L")))+

  geom_sf(data = JKsubocean,  color = "red", linewidth = 0.5, fill = NA) +
  geom_sf(data = Lsubocean, colour = "red", linewidth = 0.5, fill = NA) +
  geom_sf(data = acsurv, colour = "blue", linewidth = 0.5, fill = NA) +

  scale_x_continuous(name = "Longitude", breaks = seq(-59, -42, 4), expand = c(0,0)) +
  scale_y_continuous(name = "Latitude", breaks = seq(46, 56, 4), expand = c(0,0)) +
  
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr", which_north = "true", height = unit(0.7, "cm"), width = unit(0.7, "cm")) +
  theme(legend.position = "none")


ggsave(filename = "map.tiff", device = "tiff", plot = map, path = "./Figures",
       dpi = 300, width = 5, height = 5, units = "in")

```


# Abundance Section

## Acoustic

### Engel

```{r}
eng_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
  filter(year > 1980 & year < 1996)

## Survey year proper
p1 <- ggplot(data = eng_ac_surv) +
  geom_line(aes(x = year, y = biomass_med), colour = "#BB2D05", linewidth = 1) +
  geom_point(aes(x = year, y = biomass_med), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
  
  geom_errorbar(aes(x = year, y = biomass_med, ymin = bm_lci, ymax = bm_uci), colour = "#BB2D05", width = 0.2) +

  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.02,0), limits = c(0,9000)) +
  ggtitle("Engel Timeseries\na) 3L Spring") +
  theme_classic() +
  theme(legend.position = "none",
        axis.line.x = element_line(size = 0.5), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```

### Campelen

```{r}
camp_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
  filter(year > 1994)

## Survey year proper
p2 <- ggplot(data = camp_ac_surv) +
  geom_line(aes(x = year, y = biomass_med), colour = "#BB2D05", linewidth = 1) +
  geom_point(aes(x = year, y = biomass_med), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
  
  geom_errorbar(aes(x = year, y = biomass_med, ymin = bm_lci, ymax = bm_uci), colour = "#BB2D05", width = 0.2) +

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022.1), breaks = c(seq(1995, 2022, 5))) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.02,0), limits = c(0, 1100)) +
  ggtitle("Campelen Timeseries\nb) 3L Spring") +
  theme_classic() +
  theme(legend.position = "none",
        axis.line.x = element_line(size = 0.5), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

# Sample size

## Engel

### Spring
```{r}
load(file = "./ModelSaves/Set_Up/SE-1995.RData")

Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1995)
Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
Eghs2 <- GH_stos %>% filter(length > 40)
Eaps1 <- AP_stos %>% filter(length > 29)

Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)
Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)

```

### Fall
```{r}
load(file = "./ModelSaves/Set_Up/FE-1994.RData")

Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Eghf2 <- GH_stof %>% filter(length > 40)
Eapf1 <- AP_stof %>% filter(length > 29)

Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1988)
Eghf0 <- GH_stof %>% filter(length < 20)
Eapf0 <- AP_stof %>% filter(length < 30)

```

### Total
```{r}
Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")
Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")
Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")

```


## Campelen

### Spring
```{r}
load(file = "./ModelSaves/Set_Up/SC-2019.RData")

Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1998 & year != 2017)
Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
Cghs2 <- GH_stos %>% filter(length > 40)
Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)

Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)
Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)

```

### Fall
```{r}
# load rstrap set data
load(file = "./ModelSaves/Set_Up/FC-2020.RData")

Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Cghf2 <- GH_stof %>% filter(length > 40)
Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)

Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
Cghf0 <- GH_stof %>% filter(length < 20)
Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)

```

### Total
```{r}

Cac0 <- rbind(Cacs0, Cacf0) %>% mutate(alt.name = "Atlantic cod")
Cac1 <- rbind(Cacs1, Cacf1) %>% mutate(alt.name = "Atlantic cod")
Cac2 <- rbind(Cacs2, Cacf2) %>% mutate(alt.name = "Atlantic cod")
Cap0 <- rbind(Caps0, Capf0) %>% mutate(alt.name = "American plaice")
Cap1 <- rbind(Caps1, Capf1) %>% mutate(alt.name = "American plaice")
Cgh0 <- rbind(Cghs0, Cghf0) %>% mutate(alt.name = "Greenland halibut")
Cgh1 <- rbind(Cghs1, Cghf1) %>% mutate(alt.name = "Greenland halibut")
Cgh2 <- rbind(Cghs2, Cghf2) %>% mutate(alt.name = "Greenland halibut")

```


## All data
```{r}
# Combine seasonal data for
## Engel
Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")

Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")

Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")

## Campelen
Cac0 <- rbind(Cacs0, Cacf0) %>% mutate(alt.name = "Atlantic cod")
Cac1 <- rbind(Cacs1, Cacf1) %>% mutate(alt.name = "Atlantic cod")
Cac2 <- rbind(Cacs2, Cacf2) %>% mutate(alt.name = "Atlantic cod")

Cap0 <- rbind(Caps0, Capf0) %>% mutate(alt.name = "American plaice")
Cap1 <- rbind(Caps1, Capf1) %>% mutate(alt.name = "American plaice")

Cgh0 <- rbind(Cghs0, Cghf0) %>% mutate(alt.name = "Greenland halibut")
Cgh1 <- rbind(Cghs1, Cghf1) %>% mutate(alt.name = "Greenland halibut")
Cgh2 <- rbind(Cghs2, Cghf2) %>% mutate(alt.name = "Greenland halibut")



# Combine species data from the Engel and Campelen timeseries
Tac0 <- rbind(Eac0, Cac0)
Tac1 <- rbind(Eac1, Cac1)
Tac2 <- rbind(Eac2, Cac2)

Tap0 <- rbind(Eap0, Cap0)
Tap1 <- rbind(Eap1, Cap1)

Tgh0 <- rbind(Egh0, Cgh0)
Tgh1 <- rbind(Egh1, Cgh1)
Tgh2 <- rbind(Egh2, Cgh2)

```

## - Table 1
```{r}

sample_size <- data.frame(
  E.C.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "called"))),
  E.C.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "called"))),
  E.F.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "full"))),
  E.F.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "full"))),
  E.pcapelin =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,
                  nrow(filter(Tac1, geartype == "engel" & pa == "0"))/nrow(filter(Tac1, geartype == "engel"))*100,
                  nrow(filter(Tac2, geartype == "engel" & pa == "0"))/nrow(filter(Tac2, geartype == "engel"))*100,
                  nrow(filter(Tgh0, geartype == "engel" & pa == "0"))/nrow(filter(Tgh0, geartype == "engel"))*100,
                  nrow(filter(Tgh1, geartype == "engel" & pa == "0"))/nrow(filter(Tgh1, geartype == "engel"))*100,
                  nrow(filter(Tgh2, geartype == "engel" & pa == "0"))/nrow(filter(Tgh2, geartype == "engel"))*100,
                  nrow(filter(Tap0, geartype == "engel" & pa == "0"))/nrow(filter(Tap0, geartype == "engel"))*100,
                  nrow(filter(Tap1, geartype == "engel" & pa == "0"))/nrow(filter(Tap1, geartype == "engel"))*100),
  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & empty == TRUE))/nrow(filter(Tac0, geartype == "engel"))*100,
                nrow(filter(Tac1, geartype == "engel" & empty == TRUE))/nrow(filter(Tac1, geartype == "engel"))*100,
                nrow(filter(Tac2, geartype == "engel" & empty == TRUE))/nrow(filter(Tac2, geartype == "engel"))*100,
                nrow(filter(Tgh0, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh0, geartype == "engel"))*100,
                nrow(filter(Tgh1, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh1, geartype == "engel"))*100,
                nrow(filter(Tgh2, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh2, geartype == "engel"))*100,
                nrow(filter(Tap0, geartype == "engel" & empty == TRUE))/nrow(filter(Tap0, geartype == "engel"))*100,
                nrow(filter(Tap1, geartype == "engel" & empty == TRUE))/nrow(filter(Tap1, geartype == "engel"))*100),
  
  C.C.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "called"))),
  C.C.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "called"))),
  C.F.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "full"))),
  C.F.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "full"))),
  C.pcapelin =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,
                  nrow(filter(Tac1, geartype == "campelen" & pa == "0"))/nrow(filter(Tac1, geartype == "campelen"))*100,
                  nrow(filter(Tac2, geartype == "campelen" & pa == "0"))/nrow(filter(Tac2, geartype == "campelen"))*100,
                  nrow(filter(Tgh0, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh0, geartype == "campelen"))*100,
                  nrow(filter(Tgh1, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh1, geartype == "campelen"))*100,
                  nrow(filter(Tgh2, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh2, geartype == "campelen"))*100,
                  nrow(filter(Tap0, geartype == "campelen" & pa == "0"))/nrow(filter(Tap0, geartype == "campelen"))*100,
                  nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100),
  C.pempty = c(nrow(filter(Tac0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac0, geartype == "campelen"))*100,
                nrow(filter(Tac1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac1, geartype == "campelen"))*100,
                nrow(filter(Tac2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac2, geartype == "campelen"))*100,
                nrow(filter(Tgh0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh0, geartype == "campelen"))*100,
                nrow(filter(Tgh1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh1, geartype == "campelen"))*100,
                nrow(filter(Tgh2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh2, geartype == "campelen"))*100,
                nrow(filter(Tap0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap0, geartype == "campelen"))*100,
                nrow(filter(Tap1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap1, geartype == "campelen"))*100)

)

sample_size <- sample_size %>% mutate(E.pcapelin = format(E.pcapelin, digits = 4), C.pcapelin = format(C.pcapelin, digits = 4),
                                      E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))

write.csv(x = sample_size, file = "./Figures/samplesize.csv")

```

## Engel

### Spring

```{r}
load(file = "./ModelSaves/SprEng_Length.RData")

# Confidence intervals
low_rho = sdrep$value[names(sdrep$value) == "iye"] - qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
high_rho = sdrep$value[names(sdrep$value) == "iye"] + qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
ts_df <- data.frame(ts = rep$iye, year = sort(unique(fishy_dat$year)), low_sd = low_rho, high_sd = high_rho)

p3 <- ggplot() +
    
  geom_ribbon(data = ts_df, aes(x = year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = ts_df, aes(x = year, y = ts, colour = "all" ), linewidth = 1.5) +
  geom_point(data = ts_df, aes(x = year, y = ts, colour = "all"), size = 1.5) +
  
  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.3,2.0)) +
  scale_color_manual(name = "Species Model", values = c(all = "black"), labels = c(all = "All species")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  
  ggtitle("c) 3L Spring") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        axis.line.x = element_line(size = 0.5), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```

### Fall

```{r}
load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
load(file = "./ModelSaves/GH-FallEng_Length.RData")

# Confidence intervals for Greenland halibut model
gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_ts_df <- data.frame(ts = gh_rep$iye, time = sort(unique(gh_fishy_dat$year)), low_sd = gh_low_rho, high_sd = gh_high_rho) %>% 
  mutate(acc_year = sort(unique(gh_fishy_dat$year))+1) # since comparing fall to next year spring, lagged to year+1

# Confidence intervals for Atlantic cod/American plaice model
ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
ac_ts_df <- data.frame(ts = ac_rep$iye, time = sort(unique(ac_fishy_dat$year)), low_sd = ac_low_rho, high_sd = ac_high_rho) %>% 
  mutate(acc_year = sort(unique(ac_fishy_dat$year))+1) # since comparing fall to next year spring, lagged to year+1

p4 <- ggplot() +
  
  geom_ribbon(data = gh_ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), linewidth = 1.5) +
  geom_point(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), size = 1.5) +
  
  geom_ribbon(data = ac_ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), linewidth = 1.5) +
  geom_point(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), size = 1.5) +
  
  scale_x_continuous(name = "Year+1", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.24,0.8)) +
  scale_color_manual(name = "Species Model", 
                     values = c(ac = "#BC8DA0", gh = "#048BA8"),
                     labels = c(ac = "Cod/ Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  
  ggtitle("e) 2J3KL Fall") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        axis.line.x = element_line(size = 0.5), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

## Campelen

### Spring

```{r}
load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
load(file = "./ModelSaves/GH-SprCamp_Base.RData")

# Confidence intervals for Greenland halibut model
gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho)

# Confidence intervals for Atlantic cod/American plaice model
ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
ac_ts_df <- data.frame(ts = ac_rep$iye, time = ac_multi_inner[,1], low_sd = ac_low_rho, high_sd = ac_high_rho)

p5 <- ggplot() +
  # Taking common legend from this plot, have to make stand-in lines
  geom_line(aes(x = 0, y = 0, colour = "all"), linewidth = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
  geom_line(aes(x = 0, y = 0, colour = "ac"), linewidth = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "ac"), size = 1.5) +
  geom_line(aes(x = 0, y = 0, colour = "surv"), linewidth = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +

  
  geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), linewidth = 1.5) +
  geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
  
  geom_ribbon(data = ac_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), linewidth = 1.5) +
  geom_point(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), size = 1.5) +
  
  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.59, 2.2)) +
  scale_color_manual(name = "Species Model",
                     breaks = c("all", "surv", "ac", "gh", "ap"), 
                     values = c(all = "black", surv = "#BB2D05", ac = "#BC8DA0", gh = "#048BA8", ap = "#FF7733"),
                     labels = c(all = "All species", surv = "Acoustic survey", ac = "Cod/ Plaice", gh = "Greenland halibut", ap = "American plaice")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  
  ggtitle("d) 3L Spring") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.text = element_text(size = 15), legend.title = element_text(size = 16, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.5), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

### Fall

```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")

# Confidence intervals
low_rho = sdrep$value[names(sdrep$value) == "iye"] - qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
high_rho = sdrep$value[names(sdrep$value) == "iye"] + qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
ts_df <- data.frame(ts = rep$iye, year = sort(unique(fishy_dat$year)), low_sd = low_rho, high_sd = high_rho) %>% 
  mutate(acc_year = sort(unique(fishy_dat$year))+1) # since comparing fall to next year spring, lagged to year+1

p6 <- ggplot() +
  geom_ribbon(data = ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), linewidth = 1.5) +
  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all"), size = 1.5) +

  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.45, 1.08)) +
  scale_color_manual(name = "Species Model", values = c(all = "black"), labels = c(all = "All species")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  
  ggtitle("f) 2J3KL Fall") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        axis.line.x = element_line(size = 0.5), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```
## - Figure 3
```{r, fig.width = 16, fig.height=14}
p7 <- ggarrange(p1+theme(axis.title.x = element_blank()),
                p2+theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
                p3,
                p5+theme(axis.title.y = element_blank()),
                p4,
                p6+theme(axis.title.y = element_blank()),
                nrow = 3, ncol = 2,
                align = "v", common.legend = TRUE,
                legend = "right", legend.grob = ggpubr::get_legend(p5+theme(legend.position = "right")))

ggsave(filename = "abundancefull.tiff", device = "tiff", plot = p7, path = "./Figures",
       dpi = 300, width = 16, height = 14, units = "in")
```

# Survey Comparison

## Engel

### Spring
Spring NLFPM estimates are representative of the same year's acoustic survey biomass estimates.

Spring NLFPM: 1984-1995
Spring acoustic: 1985-1996

Correlation range: 1985-1995
```{r}
load(file = "./ModelSaves/SprEng_Length.RData")

eng_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
  filter(year > 1980 & year < 1997)

sort(unique(fishy_dat$year))[2:12]
unique(eng_ac_surv$year)[1:11]

# Set up relationship data frame
lr_dat <- data.frame(year = as.factor(seq(1985,1995,1)), 
                     acc_bm = eng_ac_surv$biomass_med[1:11], 
                     NLFPM_bm = rep$iye[2:12]) 

# Spearman correlation
cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "spearman")

```

### Fall
Fall NLFPM estimates are representative of the following year's acoustic survey biomass estimates.

Fall NLFPM: 1984-1994
Spring acoustic: 1985-1995

Correlation range: 1985-1995
```{r}
load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
load(file = "./ModelSaves/GH-FallEng_Length.RData")

eng_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
  filter(year > 1980 & year < 1996)

unique(ac_fishy_dat$year)
unique(eng_ac_surv$year)


# Set up relationship data frame - ACAP
ac_lr_dat <- data.frame(year = as.factor(seq(1985,1995,1)),
                        acc_bm = eng_ac_surv$biomass_med, 
                        NLFPM_bm = ac_rep$iye)

# Spearman correlation
cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")



# Set up relationship data frame - GH
unique(gh_fishy_dat$year)

gh_lr_dat <- data.frame(year = as.factor(seq(1985,1995,1)), 
                        acc_bm = eng_ac_surv$biomass_med, 
                        NLFPM_bm = gh_rep$iye)


# Spearman correlation
cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")

```


## Campelen

### Spring
Spring NLFPM year is acoustic survey year.

Spring NLFPM: 1996-2019
Spring acoustic: 1995-2024

Correlation range:
```{r}
load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
load(file = "./ModelSaves/GH-SprCamp_Base.RData")

camp_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
  filter(year > 1994)

unique(ac_fishy_dat$year)
unique(camp_ac_surv$year)

# Set up relationship data frame - ACAP, yr = yr
ac_lr_dat <- data.frame(year = as.factor(seq(1996,2019,1)), 
                        acc_bm = camp_ac_surv$biomass_med[2:25], 
                        NLFPM_bm = ac_rep$iye)

# Spearman correlation
cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")



# Set up relationship data frame - GH, yr = yr
unique(gh_fishy_dat$year)
gh_lr_dat <- data.frame(year = as.factor(seq(1996,2019,1)), 
                        acc_bm = camp_ac_surv$biomass_med[2:25], 
                        NLFPM_bm = gh_rep$iye)


# Spearman correlation
cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")

```

### Fall
Fall NLFPM estimates are representative of the following year's acoustic survey biomass estimates.

Fall NLFPM: 1995-2020
Spring acoustic: 1995-2024

Correlation range: 1996-2021
```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")

camp_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
  filter(year > 1994)

unique(fishy_dat$year)
unique(camp_ac_surv$year)

# Set up relationship data frame
lr_dat <- data.frame(year = as.factor(seq(1996, 2021,1)), 
                     acc_bm = camp_ac_surv$biomass_med[2:27], 
                     NLFPM_bm = rep$iye) 

# Spearman correlation
cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "spearman")

```

# y Timeseries comparison

## Engel
spring range: 1984-1995
AC fall range: 1984-1994
GH fall range: 1984-1994

Correlation ranging from 1985-1995
```{r}
load(file = "./ModelSaves/SprEng_Length.RData")
load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
load(file = "./ModelSaves/GH-FallEng_Length.RData")

# Look at year range
sort(unique(fishy_dat$year))
unique(ac_fishy_dat$year)
unique(gh_fishy_dat$year)

# Set up relationship data frame
lr_dat <- data.frame(year = as.factor(seq(1985,1995,1)), 
                     SE = rep$iye[2:12],
                     FEACAP = ac_rep$iye,
                     FEGH = gh_rep$iye)
                     

# ACAP
# Spearman correlation
cor.test(x = lr_dat$FEACAP, y = lr_dat$SE, method = "spearman")

 # GH
# Spearman correlation
cor.test(x = lr_dat$FEGH, y = lr_dat$SE, method = "spearman")

```

## Campelen
fall range: 1995-2020
acap spring range: 1996-2019
gh spring range: 1996-2019

Correlation ranging from 1996-2019
```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")
load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
load(file = "./ModelSaves/GH-SprCamp_Base.RData")

# Look at year range
unique(fishy_dat$year) # this will have to be lagged +1 yr
unique(ac_fishy_dat$year)
unique(gh_fishy_dat$year)

# Set up relationship data frame
lr_dat <- data.frame(year = as.factor(seq(1996,2019,1)), 
                     FC = rep$iye[1:24], 
                     SCACAP = ac_rep$iye, 
                     SCGH = gh_rep$iye)


# ACAP
# Spearman correlation
cor.test(x = lr_dat$FC, y = lr_dat$SCACAP, method = "spearman")


# GH
# Spearman correlation
cor.test(x = lr_dat$FC, y = lr_dat$SCGH, method = "spearman")

```

# y+1 Timeseries comparison

## Engel
spring range: 1984-1995
AC fall range: 1984-1994
GH fall range: 1984-1994

Correlation ranging from 1984-1994
```{r}
load(file = "./ModelSaves/SprEng_Length.RData")
load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
load(file = "./ModelSaves/GH-FallEng_Length.RData")

# Look at year range
sort(unique(fishy_dat$year))
unique(ac_fishy_dat$year)
unique(gh_fishy_dat$year)

# Set up relationship data frame
lr_dat <- data.frame(year = as.factor(seq(1984,1994,1)), 
                     SE = rep$iye[1:11],
                     FEACAP = ac_rep$iye,
                     FEGH = gh_rep$iye)


# ACAP
# Spearman correlation
cor.test(x = lr_dat$FEACAP, y = lr_dat$SE, method = "spearman")

# GH
# Spearman correlation
cor.test(x = lr_dat$FEGH, y = lr_dat$SE, method = "spearman")

```

## Campelen
fall range: 1995-2020
acap spring range: 1996-2019
gh spring range: 1996-2019

Correlation ranging from 1996-2019
```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")
load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
load(file = "./ModelSaves/GH-SprCamp_Base.RData")

# Look at year range
unique(fishy_dat$year)[2:25]
unique(ac_fishy_dat$year)
unique(gh_fishy_dat$year)

# Set up relationship data frame
lr_dat <- data.frame(year = as.factor(seq(1996,2019,1)), 
                     FC = rep$iye[2:25], 
                     SCACAP = ac_rep$iye, 
                     SCGH = gh_rep$iye)


# ACAP
# Spearman correlation
cor.test(x = lr_dat$FC, y = lr_dat$SCACAP, method = "spearman")


# GH
# Spearman correlation
cor.test(x = lr_dat$FC, y = lr_dat$SCGH, method = "spearman")

```


