---
output: html_document
editor_options: 
  chunk_output_type: inline
---
# Setup Env

```{r include=FALSE}
library(tidyverse)
library(cowplot)
library(ggpubr)
library(TMB)
```

# Sample size

## Engel

### Spring
```{r}
load(file = "./ModelSaves/Set_Up/SE-1995.RData")

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
aps1 <- AP_stos %>% filter(length > 29)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)

acs0 <- AC_stos %>% filter(length < 18)
aps0 <- AP_stos %>% filter(length < 30)
ghs0 <- GH_stos %>% filter(length < 20)


# table(acs0$pa, acs0$year)
# table(acs1$pa, acs1$year)
# table(acs2$pa, acs2$year)
# table(aps0$pa, aps0$year)
# table(aps1$pa, aps1$year)
# table(ghs0$pa, ghs0$year)
# table(ghs1$pa, ghs1$year)
# table(ghs2$pa, ghs2$year)

```

### Fall
```{r}
load(file = "./ModelSaves/Set_Up/FE-1994.RData")

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
apf1 <- AP_stof %>% filter(length > 29)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)

acf0 <- AC_stof %>% filter(length < 18)
apf0 <- AP_stof %>% filter(length < 30)
ghf0 <- GH_stof %>% filter(length < 20)


# table(acf0$pa, acf0$year)
# table(acf1$pa, acf1$year)
# table(acf2$pa, acf2$year)
# table(apf0$pa, apf0$year)
# table(apf1$pa, apf1$year)
# table(ghf0$pa, ghf0$year)
# table(ghf1$pa, ghf1$year)
# table(ghf2$pa, ghf2$year)

```

### Yearly of all data in both seasons
```{r}
Eac0 <- rbind(acs0, acf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(acs1, acf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(acs2, acf2) %>% mutate(alt.name = "Atlantic cod")
Eap0 <- rbind(aps0, apf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(aps1, apf1) %>% mutate(alt.name = "American plaice")
Egh0 <- rbind(ghs0, ghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(ghs1, ghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(ghs2, ghf2) %>% mutate(alt.name = "Greenland halibut")

# table(Eac0$year, Eac0$season)
# table(Eac1$year, Eac1$season)
# table(Eac2$year, Eac2$season)
# table(Egh0$year, Egh0$season)
# table(Egh1$year, Egh1$season)
# table(Egh2$year, Egh2$season)
# table(Eap0$year, Eap0$season)
# table(Eap1$year, Eap1$season)

```


## Campelen

### Spring
```{r}
load(file = "./ModelSaves/Set_Up/SC-2019.RData")


acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
aps1 <- AP_stos %>% filter(length > 29)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)

acs0 <- AC_stos %>% filter(length < 18)
aps0 <- AP_stos %>% filter(length < 30)
ghs0 <- GH_stos %>% filter(length < 20)


# table(acs0$pa, acs0$year)
# table(acs1$pa, acs1$year)
# table(acs2$pa, acs2$year)
# table(aps0$pa, aps0$year)
# table(aps1$pa, aps1$year)
# table(ghs0$pa, ghs0$year)
# table(ghs1$pa, ghs1$year)
# table(ghs2$pa, ghs2$year)

```

### Fall
```{r}
# load rstrap set data
load(file = "./ModelSaves/Set_Up/FC-2020.RData")


acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
apf1 <- AP_stof %>% filter(length > 29)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)

acf0 <- AC_stof %>% filter(length < 18)
apf0 <- AP_stof %>% filter(length < 30)
ghf0 <- GH_stof %>% filter(length < 20)


# table(acf0$pa, acf0$year)
# table(acf1$pa, acf1$year)
# table(acf2$pa, acf2$year)
# table(apf0$pa, apf0$year)
# table(apf1$pa, apf1$year)
# table(ghf0$pa, ghf0$year)
# table(ghf1$pa, ghf1$year)
# table(ghf2$pa, ghf2$year)

```

### Yearly of all data in both seasons
```{r}

Cac0 <- rbind(acs0, acf0) %>% mutate(alt.name = "Atlantic cod")
Cac1 <- rbind(acs1, acf1) %>% mutate(alt.name = "Atlantic cod")
Cac2 <- rbind(acs2, acf2) %>% mutate(alt.name = "Atlantic cod")
Cap0 <- rbind(aps0, apf0) %>% mutate(alt.name = "American plaice")
Cap1 <- rbind(aps1, apf1) %>% mutate(alt.name = "American plaice")
Cgh0 <- rbind(ghs0, ghf0) %>% mutate(alt.name = "Greenland halibut")
Cgh1 <- rbind(ghs1, ghf1) %>% mutate(alt.name = "Greenland halibut")
Cgh2 <- rbind(ghs2, ghf2) %>% mutate(alt.name = "Greenland halibut")

```


## - Table S1 and S2
```{r}

# Combine species data from the Engel and Campelen timeseries
Tac0 <- rbind(Eac0, Cac0)
Tac1 <- rbind(Eac1, Cac1)
Tac2 <- rbind(Eac2, Cac2)

Tap0 <- rbind(Eap0, Cap0)
Tap1 <- rbind(Eap1, Cap1)

Tgh0 <- rbind(Egh0, Cgh0)
Tgh1 <- rbind(Egh1, Cgh1)
Tgh2 <- rbind(Egh2, Cgh2)



# Turn into dataframe
dfac0 <- reshape(data.frame(table(Tac0$year, Tac0$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(ac0_spring = Freq.spring, ac0_fall = Freq.fall)
dfgh0 <- reshape(data.frame(table(Tgh0$year, Tgh0$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(gh0_spring = Freq.spring, gh0_fall = Freq.fall)
dfap0 <- reshape(data.frame(table(Tap0$year, Tap0$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>%  
  rename(ap0_spring = Freq.spring, ap0_fall = Freq.fall)

dfac1 <- reshape(data.frame(table(Tac1$year, Tac1$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(ac1_spring = Freq.spring, ac1_fall = Freq.fall)
dfac2 <- reshape(data.frame(table(Tac2$year, Tac2$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(ac2_spring = Freq.spring, ac2_fall = Freq.fall)

dfgh1 <- reshape(data.frame(table(Tgh1$year, Tgh1$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(gh1_spring = Freq.spring, gh1_fall = Freq.fall)
dfgh2 <- reshape(data.frame(table(Tgh2$year, Tgh2$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(gh2_spring = Freq.spring, gh2_fall = Freq.fall)
dfap1 <- reshape(data.frame(table(Tap1$year, Tap1$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(ap1_spring = Freq.spring, ap1_fall = Freq.fall)


ac <- data.frame(year = seq(1984,2020,1), 
                 ac0_spring = c(dfac0$ac0_spring[1:9], rep(0,2), dfac0$ac0_spring[10:35]),
                 ac1_spring = c(dfac1$ac1_spring),
                 ac2_spring = c(dfac2$ac2_spring),
                 
                 ac0_fall = c(dfac0$ac0_fall[1:9], rep(0,2), dfac0$ac0_fall[10:35]),
                 ac1_fall = c(dfac1$ac1_fall),
                 ac2_fall = c(dfac2$ac2_fall))
write.csv(ac, file = "./Extra/acseason.csv")


gh <- data.frame(year = seq(1984,2020,1), 
                 gh0_spring = c(dfgh0$gh0_spring),
                 gh1_spring = c(dfgh1$gh1_spring),
                 gh2_spring = c(dfgh2$gh2_spring),
                 
                 gh0_fall = c(dfgh0$gh0_fall),
                 gh1_fall = c(dfgh1$gh1_fall),
                 gh2_fall = c(dfgh2$gh2_fall))
write.csv(gh, file = "./Extra/ghseason.csv")


ap <- data.frame(year = seq(1984,2020,1), 
                 ap0_spring = c(dfap0$ap0_spring),
                 ap1_spring = c(dfap1$ap1_spring),
                 
                 ap0_fall = c(dfap0$ap0_fall),
                 ap1_fall = c(dfap1$ap1_fall))
write.csv(ap, file = "./Extra/apseason.csv")

```

# Annual input trends

## Engel

### Spring

```{r}

load(file = "./ModelSaves/ACAP-SprEng_Length.RData")
load(file = "./ModelSaves/GH-SprEng_Length.RData")

# Set up index df - GH
gh_data <- gh_fishy_dat
gh_uni_names <- unique(gh_data$names)
gh_dat_names <- c("Index", gh_uni_names)

gh_new_list <- list()
for(i in 1:length(gh_uni_names)){
  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
}

gh_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  gh_new_list
)

#Functional Response equation
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- ((gh_multi_inner[ ,i+2]*(gh_rep$chi[i]^gh_rep$beta[i]))/(1-gh_multi_inner[ ,i+2]))^(1/gh_rep$beta[i])
}

# Reverse log transform input values
gh_multi_inner[,2] <- log(1/(1-gh_multi_inner[ ,2]))
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- log(1/(1-gh_multi_inner[ ,i+(length(gh_uni_names)+1)])) # produces NAs but not to worry about
}



# Set up index df - AC
ac_data <- ac_fishy_dat
ac_uni_names <- unique(ac_data$names)
ac_dat_names <- c("Index", ac_uni_names)

ac_new_list <- list()
for(i in 1:length(ac_uni_names)){
  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
}

ac_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  ac_new_list
)


#Functional Response equation
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- ((ac_multi_inner[ ,i+2]*(ac_rep$chi[i]^ac_rep$beta[i]))/(1-ac_multi_inner[ ,i+2]))^(1/ac_rep$beta[i])
}

# Reverse log transform input values
ac_multi_inner[,2] <- log(1/(1-ac_multi_inner[ ,2])) # have to transform trawl separately bc at start of df
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- log(1/(1-ac_multi_inner[ ,i+(length(ac_uni_names)+1)])) # produces NAs but not to worry about
}




# Add all input data into one dataframe
plotdf <- data.frame(time = gh_multi_inner[,1], 
                     ts = gh_multi_inner[,2],
                     ac1 = ac_multi_inner[,6], 
                     ac2 = ac_multi_inner[,7],
                     gh1 = gh_multi_inner[,5],
                     gh2 = gh_multi_inner[,6],
                     ap1 = ac_multi_inner[,8]
                     )


# plot
se <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +
  
  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +
  
  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +
  
  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +
  
  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("Engel\na) 3L Spring") + 
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank(), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))



```

### Fall

```{r, fig.width=10, fig.height=8}

load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
load(file = "./ModelSaves/GH-FallEng_Length.RData")

# Set up index df - GH
gh_data <- gh_fishy_dat
gh_uni_names <- unique(gh_data$names)
gh_dat_names <- c("Index", gh_uni_names)

gh_new_list <- list()
for(i in 1:length(gh_uni_names)){
  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
}

gh_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  gh_new_list
)

#Functional Response equation
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- ((gh_multi_inner[ ,i+2]*(gh_rep$chi[i]^gh_rep$beta[i]))/(1-gh_multi_inner[ ,i+2]))^(1/gh_rep$beta[i])
}

# Reverse log transform input values
gh_multi_inner[,2] <- log(1/(1-gh_multi_inner[ ,2]))
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- log(1/(1-gh_multi_inner[ ,i+(length(gh_uni_names)+1)])) # produces NAs but not to worry about
}



# Set up index df - AC
ac_data <- ac_fishy_dat
ac_uni_names <- unique(ac_data$names)
ac_dat_names <- c("Index", ac_uni_names)

ac_new_list <- list()
for(i in 1:length(ac_uni_names)){
  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
}

ac_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  ac_new_list
)


#Functional Response equation
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- ((ac_multi_inner[ ,i+2]*(ac_rep$chi[i]^ac_rep$beta[i]))/(1-ac_multi_inner[ ,i+2]))^(1/ac_rep$beta[i])
}

# Reverse log transform input values
ac_multi_inner[,2] <- log(1/(1-ac_multi_inner[ ,2])) # have to transform trawl separately bc at start of df
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- log(1/(1-ac_multi_inner[ ,i+(length(ac_uni_names)+1)])) # produces NAs but not to worry about
}




# Add all input data into one dataframe
plotdf <- data.frame(time = gh_multi_inner[,1], 
                     ts = gh_multi_inner[,2],
                     ac1 = ac_multi_inner[,6], 
                     ac2 = ac_multi_inner[,7],
                     gh1 = gh_multi_inner[,5],
                     gh2 = gh_multi_inner[,6],
                     ap1 = ac_multi_inner[,8]
                     )


# plot
fe <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +
  
  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +
  
  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +
  
  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +
  
  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("c) 2J3KL Fall") + 
  theme_classic() +
  theme(legend.position = "none",
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))


```

## Campelen

### Spring

```{r Fall Campelen, fig.height=8, fig.width=10}

load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
load(file = "./ModelSaves/GH-SprCamp_Base.RData")


# Set up index df - GH
gh_data <- gh_fishy_dat
gh_uni_names <- unique(gh_data$names)
gh_dat_names <- c("Index", gh_uni_names)

gh_new_list <- list()
for(i in 1:length(gh_uni_names)){
  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
}

gh_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  gh_new_list
)

#Functional Response equation
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- ((gh_multi_inner[ ,i+2]*(gh_rep$chi[i]^gh_rep$beta[i]))/(1-gh_multi_inner[ ,i+2]))^(1/gh_rep$beta[i])
}

# Reverse log transform input values
gh_multi_inner[,2] <- log(1/(1-gh_multi_inner[ ,2]))
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- log(1/(1-gh_multi_inner[ ,i+(length(gh_uni_names)+1)])) # produces NAs but not to worry about
}



# Set up index df - AC
ac_data <- ac_fishy_dat
ac_uni_names <- unique(ac_data$names)
ac_dat_names <- c("Index", ac_uni_names)

ac_new_list <- list()
for(i in 1:length(ac_uni_names)){
  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
}

ac_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  ac_new_list
)


#Functional Response equation
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- ((ac_multi_inner[ ,i+2]*(ac_rep$chi[i]^ac_rep$beta[i]))/(1-ac_multi_inner[ ,i+2]))^(1/ac_rep$beta[i])
}

# Reverse log transform input values
ac_multi_inner[,2] <- log(1/(1-ac_multi_inner[ ,2])) # have to transform trawl separately bc at start of df
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- log(1/(1-ac_multi_inner[ ,i+(length(ac_uni_names)+1)])) # produces NAs but not to worry about
}




# Add all input data into one dataframe
plotdf <- data.frame(time = gh_multi_inner[,1], 
                     ts = gh_multi_inner[,2],
                     ac = ac_multi_inner[,5], 
                     gh = gh_multi_inner[,4],
                     ap = ac_multi_inner[,6]
                     )


# plot
sc <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +
  
  geom_line( aes(x = time, y = ac, colour = "ac", linetype = "medium"), size = 1.4) +
  
  geom_line(aes(x = time, y = gh, colour = "gh", linetype = "medium"), size = 1.4) +
  
  geom_line(aes(x = time, y = ap, colour = "ap", linetype = "medium"), size = 1.4) +
  
  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.82, 2.3)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("Campelen\nb) 3L Spring") + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```

### Fall

```{r Fall Campelen, fig.height=8, fig.width=10}

load(file = "./ModelSaves/FallCamp_Length.RData")

data <- fishy_dat

uni_names <- unique(data$names)
dat_names <- c("Index", uni_names)

new_list <- list()

for(i in 1:length(uni_names)){
  one_dex <- subset(data, names == uni_names[i])
  new_list[[i]] <- aggregate(one_dex$pa, by = list(one_dex$year), FUN = mean, na.rm = TRUE)
}

multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  new_list
)

#Functional Response equation
for(i in 1:(length(uni_names)-1)){
  multi_inner[,i+(length(uni_names)+1)] <- ((multi_inner[ ,i+2]*(rep$chi[i]^rep$beta[i]))/(1-multi_inner[ ,i+2]))^(1/rep$beta[i])
}

# Reverse log transform input values
multi_inner[,2] <- log(1/(1-multi_inner[ ,2]))
for(i in 1:(length(uni_names)-1)){
  multi_inner[,i+(length(uni_names)+1)] <- log(1/(1-multi_inner[ ,i+(length(uni_names)+1)])) # produces NAs but not to worry about
}


# Add all input data into one dataframe
plotdf <- data.frame(time = multi_inner[,1], 
                     ts = multi_inner[,2],
                     ac1 = multi_inner[,8], 
                     ac2 = multi_inner[,9],
                     gh1 = multi_inner[,10],
                     gh2 = multi_inner[,11],
                     ap1 = multi_inner[,12]
                     )


# plot
fc <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +
  
  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +
  
  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +
  
  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +
  
  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.32, 1.6)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("d) 2J3KL Fall") + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))


```
## - Figure S1
```{r, fig.height=10, fig.width=12}

p1 <- ggarrange(se,
          sc,
          fe,
          fc,
          nrow = 2, ncol = 2,
          align = "v", common.legend = TRUE,
          legend = "right", legend.grob = ggpubr::get_legend(fc+theme(legend.position = "right", legend.text = element_text(size = 15),)))

ggsave(filename = "inputdata.tiff", device = "tiff", plot = p1, path = "./Figures",
       dpi = 300, width = 14, height = 10, units = "in")


```

# Residuals

## - Figure S2
```{r, fig.width=5, fig.height=4}
source(file = "./Analysis/Campelen/Fall/FallCamp_Length.R")

sim_response <- replicate(250, obj$simulate()$pa)

sim_res <- DHARMa::createDHARMa(simulatedResponse = sim_response, observedResponse = tmb_data$pa, fittedPredictedResponse = rep$new_mu)

DHARMa::plotQQunif(sim_res, testUniformity=F, testDispersion = F, testOutliers = F)

DHARMa::plotResiduals(sim_res, form = as.factor(tmb_data$idex))

DHARMa::plotResiduals(sim_res, form = as.factor(tmb_data$iyear))

```

# Functional response
## - Table S4
```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")

beta_est <- as.numeric(sdrep$value[names(sdrep$value) == "beta"])
chi_est <- as.numeric(sdrep$value[names(sdrep$value) == "chi"])

# CI
beta_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "beta"])
beta_low <- vector()
beta_high <- vector()
for(i in 1:length(beta_sd)){
  beta_low[i] <- beta_est[i] - qnorm(0.975)*beta_sd[i]
  beta_high[i] <- beta_est[i] + qnorm(0.975)*beta_sd[i]}

chi_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "chi"])
chi_low <- vector()
chi_high <- vector()
for(i in 1:length(chi_sd)){
  chi_low[i] <- chi_est[i] - qnorm(0.975)*chi_sd[i]
  chi_high[i] <- chi_est[i] + qnorm(0.975)*chi_sd[i]}


param_estimate <- data.frame(
  estimate = c(
    format(beta_est[1], digits = 4),format(chi_est[1], digits = 4),
    format(beta_est[2], digits = 4),format(chi_est[2], digits = 4),
    format(beta_est[3], digits = 4),format(chi_est[3], digits = 4), 
    format(beta_est[4], digits = 4),format(chi_est[4], digits = 4), 
    format(beta_est[5], digits = 4),format(chi_est[5], digits = 4)),
  CI = c(
    paste("[", format(beta_low[1], digits = 3), ",", format(beta_high[1], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[1], digits = 3), ",", format(chi_high[1], digits = 3), "]", sep = ""),
    paste("[", format(beta_low[2], digits = 3), ",", format(beta_high[2], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[2], digits = 3), ",", format(chi_high[2], digits = 3), "]", sep = ""),
    paste("[", format(beta_low[3], digits = 3), ",", format(beta_high[3], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[3], digits = 3), ",", format(chi_high[3], digits = 3), "]", sep = ""),
    paste("[", format(beta_low[4], digits = 3), ",", format(beta_high[4], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[4], digits = 3), ",", format(chi_high[4], digits = 3), "]", sep = ""),
    paste("[", format(beta_low[5], digits = 3), ",", format(beta_high[5], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[5], digits = 3), ",", format(chi_high[5], digits = 3), "]", sep = ""))
)


write.csv(x = param_estimate, file = "./Figures/frestimates.csv")

```

## - Figure S4
```{r, fig.width=5, fig.height=5}
load(file = "./ModelSaves/FallCamp_Length.RData")

# Setup df for FR curve
newx <- seq(from = 0, to = 1, by = 0.001)

## set estimates
beta_est <- as.numeric(sdrep$value[names(sdrep$value) == "beta"])
chi_est <- as.numeric(sdrep$value[names(sdrep$value) == "chi"])

idmod <- unique(rep$idmod)

rate <- list()
for(i in 1:length(beta_est)){
  rate[[i]] <- ((1*(newx^beta_est[i]))/((chi_est[i]^beta_est[i])+(newx^beta_est[i])))
}

# CI
## format standard deviation
beta_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "beta"])
## generate confidence intervals
beta_low <- vector()
beta_high <- vector()
for(i in 1:length(beta_sd)){
  beta_low[i] <- beta_est[i] - qnorm(0.975)*beta_sd[i]
  beta_high[i] <- beta_est[i] + qnorm(0.975)*beta_sd[i]
}

## format standard deviation
chi_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "chi"])
## generate confidence intervals
chi_low <- vector()
chi_high <- vector()
for(i in 1:length(chi_sd)){
  chi_low[i] <- chi_est[i] - qnorm(0.975)*chi_sd[i]
  chi_high[i] <- chi_est[i] + qnorm(0.975)*chi_sd[i]
}

rate_high <- list()
rate_low <- list()
for(i in 1:length(beta_est)){
  rate_high[[i]] <- ((1*(newx^beta_high[i]))/((chi_high[i]^beta_high[i])+(newx^beta_high[i])))
  rate_low[[i]] <- ((1*(newx^beta_low[i]))/((chi_low[i]^beta_low[i])+(newx^beta_low[i])))
}



ggplot() +
  geom_line(aes(x = newx, y = rate[[1]], colour = "ac", linetype = "c1"), linewidth = 0.8) +
  geom_line(aes(x = newx, y = rate[[2]], colour = "ac", linetype = "c2"), linewidth = 0.8) +
  geom_line(aes(x = newx, y = rate[[3]], colour = "gh", linetype = "c1"), linewidth = 0.8) +
  geom_line(aes(x = newx, y = rate[[4]], colour = "gh", linetype = "c2"), linewidth = 0.8) +
  geom_line(aes(x = newx, y = rate[[5]], colour = "ap", linetype = "c2"), linewidth = 0.8) +

  scale_x_continuous(name = "Relative prey density", limits = c(0,1.02), breaks = c(seq(0,1,0.5)), expand = c(0,0)) +
  scale_y_continuous(name = "Probability of consumption", limits = c(0,1.01), breaks = c(seq(0,1,0.5)), expand = c(0,0)) +
  scale_color_manual(name = "Species", values = c(ac = "#A4243B", gh = "#048BA8", ap = "#FF7733"),
                     labels = c(ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "Length category", , values = c(c1 = "solid", c2 = "dotdash"),
                        labels = c(c1 = "Medium", c2 = "Large")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm"),
         linetype = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = c(0.35,0.68), legend.direction = "vertical", legend.spacing.y = unit(.1, 'cm'), 
        legend.text = element_text(size = 15), legend.title = element_text(size = 16, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.5), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
)

ggsave(filename = "bestfr.tiff", device = "tiff", plot = last_plot(), path = "./Figures",
       dpi = 300, width = 5, height = 5, units = "in")

```

# Predator feeding ranges

## Spring Engel

```{r}
source("./Analysis/Engel/Spring/SprEng-SetUp.R")

pTSE <- ggplot(stom_spr_good) +
  geom_boxplot(aes(x = alt.name, y = bot.temp)) +
  
  scale_x_discrete(name = "Predator species") +
  scale_y_continuous(name = "Bottom temperature (°C)", limits = c(min(stom_spr_good$bot.temp)-0.1, max(stom_spr_good$bot.temp)+0.1)) +
  
  theme_classic() +
  theme(axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), axis.title.x = element_blank(),
        legend.text = element_text(size = 13), legend.title = element_text(size = 14)
  )

```

## Fall Engel

```{r}
source("./Analysis/Engel/Fall/FallEng-SetUp.R")

pTFE <- ggplot(stom_fall_good) +
  geom_boxplot(aes(x = alt.name, y = bot.temp)) +
  
  scale_x_discrete(name = "Predator species") +
  scale_y_continuous(name = "Bottom temperature (°C)", limits = c(min(stom_fall_good$bot.temp)-0.1, max(stom_fall_good$bot.temp)+0.1)) +
  
  theme_classic() +
  theme(axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        legend.text = element_text(size = 13), legend.title = element_text(size = 14)
  )
        
```

## Spring Campelen

```{r}
source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")

pTSC <- ggplot(stom_spr_good) +
  geom_boxplot(aes(x = alt.name, y = bot.temp)) +
  
  scale_x_discrete(name = "Predator species") +
  scale_y_continuous(name = "Bottom temperature (°C)", limits = c(min(stom_spr_good$bot.temp)-0.1, max(stom_spr_good$bot.temp)+0.1)) +
  
  theme_classic() +
  theme(axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        legend.text = element_text(size = 13), legend.title = element_text(size = 14)
  )

```

## Fall Campelen

```{r}
source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")

pTFC <- ggplot(stom_fall_good) +
  geom_boxplot(aes(x = alt.name, y = bot.temp)) +
  
  scale_x_discrete(name = "Predator species") +
  scale_y_continuous(name = "Bottom temperature (°C)", limits = c(min(stom_fall_good$bot.temp)-0.1, max(stom_fall_good$bot.temp)+0.1)) +
  
  theme_classic() +
  theme(axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), axis.title.y = element_blank(),
        legend.text = element_text(size = 13), legend.title = element_text(size = 14)
  )

```
## - Figure S4
```{r, fig.width=10.5, fig.height=8}
ggpubr::ggarrange(pTSE+ggtitle("Engel\na) 3L Spring")+theme(plot.title = element_text(face = "bold")),
                  pTSC+ggtitle("Campelen\nb) 3L Spring")+theme(plot.title = element_text(face = "bold")),
                  pTFE+ggtitle("c) 2J3KL Fall")+theme(plot.title = element_text(face = "bold")),
                  pTFC+ggtitle("d) 2J3KL Fall")+theme(plot.title = element_text(face = "bold"))
  
)

ggsave(filename = "tempranges.tiff", device = "tiff", plot = last_plot(), path = "./Figures",
       dpi = 300, width = 10.5, height = 8, units = "in")

```


# Full into Called
First, we reduce Full stomach data to Called data by determining top two prey species in a stomach.
Then, we are comparing the frequency of top-two full stomach data to any occurrence of capelin in stomachs
```{r, fig.width=10}
# source(file = "./Analysis/FullStomach_process.R")
load(file = "./Data/uni_full_stom.RData")

#add capelin presence/absence
new_full_stom <- uni_full_stom %>% mutate(cap_pa = ifelse(prey1 == "Capelin"|prey2 == "Capelin", 1, 0)) %>% 
  mutate(cap_pa = ifelse(prey1 != "Capelin" & is.na(prey2) == T, 0, cap_pa),
         season = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "Spring", "Fall"),
         alt.name = SPECIES,
         alt.name = ifelse(alt.name == "889", "American plaice", alt.name),
         alt.name = ifelse(alt.name == "438", "Atlantic cod", alt.name),
         alt.name = ifelse(alt.name == "892", "Greenland halibut", alt.name))


#look at old capelin presence/absence over time
old_full_stom <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% filter(YEAR >= 1984) %>%
  mutate(cap_pa = ifelse(PREY_CAP == "Capelin", 1, 0),
         season = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "Spring", "Fall"),
         alt.name = SPECIES,
         alt.name = ifelse(alt.name == "889", "American plaice", alt.name),
         alt.name = ifelse(alt.name == "438", "Atlantic cod", alt.name),
         alt.name = ifelse(alt.name == "892", "Greenland halibut", alt.name))



#calculate frequency of capelin presence by year

new_full_freq <- new_full_stom %>% group_by(YEAR, season, alt.name, cap_pa) %>% 
  summarise(n = n()) %>% 
  mutate(freq = n/sum(n)) %>%
  filter(cap_pa == 1 & YEAR >= 1984 & YEAR <= 2021) %>%
  rbind(data.frame(YEAR = c(1986, seq(1988, 2007, 1)), alt.name = rep("American plaice", 21), season = rep("Fall", 21))) %>%
  rbind(data.frame(YEAR = seq(1987, 2012, 1), alt.name = rep("American plaice", 26), season = rep("Spring", 26))) %>%
  
  rbind(data.frame(YEAR = seq(1996, 2007, 1), alt.name = rep("Atlantic cod", 12), season = rep("Fall", 12))) %>%
  rbind(data.frame(YEAR = seq(1998, 2012, 1), alt.name = rep("Atlantic cod", 15), season = rep("Spring", 15))) %>%
  
  rbind(data.frame(YEAR = c(1984, seq(1986, 2012, 1)), alt.name = rep("Greenland halibut", 28), season = rep("Spring", 28)))
  


old_full_freq <- old_full_stom %>% group_by(YEAR, season, alt.name, cap_pa) %>% 
  summarise(n = n()) %>% 
  mutate(freq = n/sum(n)) %>%
  filter(cap_pa == 1 & YEAR >= 1984 & YEAR <= 2021) %>%
  rbind(data.frame(YEAR = c(1986, seq(1988, 2007, 1)), alt.name = rep("American plaice", 21), season = rep("Fall", 21))) %>%
  rbind(data.frame(YEAR = seq(1987, 2012, 1), alt.name = rep("American plaice", 26), season = rep("Spring", 26))) %>%
  
  rbind(data.frame(YEAR = seq(1996, 2007, 1), alt.name = rep("Atlantic cod", 12), season = rep("Fall", 12))) %>%
  rbind(data.frame(YEAR = seq(1998, 2012, 1), alt.name = rep("Atlantic cod", 15), season = rep("Spring", 15))) %>%
  
  rbind(data.frame(YEAR = c(1984, seq(1986, 2012, 1)), alt.name = rep("Greenland halibut", 28), season = rep("Spring", 28)))


```

## - Figure Reviewer comment
```{r}
ggplot() +
  geom_point(data = old_full_freq, aes(x = YEAR, y = freq, colour = 'old')) +
  geom_line(data = old_full_freq, aes(x = YEAR, y = freq, colour = 'old')) +
  
  geom_point(data = new_full_freq, aes(x = YEAR, y = freq, colour = 'new')) +
  geom_line(data = new_full_freq, aes(x = YEAR, y = freq, colour = 'new')) +
  
  facet_grid(rows = vars(season), cols = vars(alt.name)) + 
  
  scale_x_continuous(name = "Year", breaks = c(seq(1985,2021,5))) +
  scale_y_continuous(name = "Frequency of occurrence") + 
  scale_color_manual(name = "Dataseries", 
                     values = c(old = "red", new = 'blue'),
                     labels = c(old = "Any observation", new = "Top two prey")) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.title = element_text(size = 13, face = "bold"), legend.text = element_text(size = 12), strip.text = element_text(size = 12),
        axis.title = element_text(size = 15, face = "bold"), axis.text = element_text(size = 14))

ggsave(filename = "FullComparison.tiff", device = "tiff", plot = last_plot(), path = "./Figures",
       dpi = 300, width = 15, height = 10, units = "in")

```
