---
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r include=FALSE}
library(tidyverse)
library(glmmTMB)
library(ggeffects)
```

# AR1

## Campelen

### Fall

```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

lr_dat <- data.frame(year = as.factor(acc_surv[2:28,1]), acc_bm = acc_surv[2:28,2], NLFPM_bm = rep$iye)

cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "spearman")

```
Fall Campelen NLFPM correlation to acoustic - not significant positive relationship (rho = 0.4287, p = 0.05927)


### Spring

```{r}
load(file = "./ModelSaves/AP-SprCamp_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

ap_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = ap_rep$iye)

# # Influential points
# ap_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
#                         NLFPM_bm = c(ap_rep$iye[2:18],ap_rep$iye[21:25]))

cor.test(x = ap_lr_dat$NLFPM_bm, y = ap_lr_dat$acc_bm, method = "spearman")

```
Spring Campelen AP NLFPM correlation to acoustic - not significant negative relationship (Corr = -0.097, p = 0.684)


```{r}
load(file = "./ModelSaves/GH-SprCamp_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)


gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye)

cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")

```
Spring Campelen GH NLFPM correlation to acoustic - not significant negative relationship (Corr = -0.3693, p = 0.109)

## Engel

### Fall
```{r}
load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.) 

# Set up relationship data frame - ACAP
ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = ac_rep$iye) #have to y+1

cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")

```
Fall Engel ACAP NLFPM correlation to acoustic - significant positive relationship (Corr = 0.5272, p = 0.1447)

```{r}
load(file = "./ModelSaves/GH-FallEng_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.) 

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = gh_rep$iye)

cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")

```
Fall Engel GH NLFPM correlation to acoustic - significant positive relationship (rho = 0.6862, p = 0.04124)

### Spring

```{r}
load(file = "./ModelSaves/ACAP-SprEng_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1983 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(ac_rep$iye[12], ac_rep$iye[1:11])) #have to y+1

cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")

```
Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (rho = 0.0838, p = 0.8435)

```{r}
load(file = "./ModelSaves/GH-SprEng_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1983 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(gh_rep$iye[12], gh_rep$iye[1:11]))

cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")

```
Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (rho = 0.1198, p = 0.7776)

